---
title: "K-Pop vs Western Pop"
author: "Shankar Rai"
date: "`r Sys.Date()`"
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(flexdashboard)
library(tidyverse)
library(spotifyr)
library(ggplot2)
library(plotly)
library(compmus)

westernPop <- get_playlist_audio_features("", "3lro0N5fTyoXFZFbowlcdM")
westernPop <- westernPop[!is.na(westernPop$tempo), ][1:100,]
koreanPop <- get_playlist_audio_features("", "30EtqO7XgA36lwcdj1Uuex")
allPop <- rbind(westernPop, koreanPop)
```

### Introduction

Repository for Computational Musicology 2022.\
Name: Shankar Rai, Student number: 12520667. \
PLEASE DO NOT SHOW THIS PORTFOLIO IN CLASS.

For the corpus the 100 most popular western pop music of 2010 - 2020 and the 100 most popular Korean pop (K-pop) music of the recent years will be used. I chose those as I am interested in both of these genres and I listen to them a lot. Therefore I am interested in the similarities and differences between sounds in these genres as K-pop is becoming more and more popular in western countries. I expect there to be differences in the tempo, energy and danceability.

As the corpus makes use of the top 100, of both genres in recent years I would argue that they represent both genres pretty well. One of the weaknesses of the corpus are that it makes use of a list not created by spotify itself. Therefore it may not be an absolute top 100. Another weakness may be that the western list is not only English based, but may also contain Latin influences. One extra thing to mark is that some K-pop songs are collaborations with western artist.

Some typical track from the western list are: "Shape of You, Ed Sheeran", "Sugar, Maroon 5", "Can't feel my face, The Weeknd". Some typical K-pop tracks are "Dynamite, BTS", "I cant"t stop me, Twice", "Kill This Love, BLACKPINK". These are typical songs as these are from some of the biggest artist in their respective genres. Some interesting songs are: "More, KD/A" and "Kiss and Make Up, "Dua Lipa, BLACKPINK" as these are collaborated songs with Korean and western artists.

Links to the playlists:\
[Western pop]("https://open.spotify.com/playlist/3lro0N5fTyoXFZFbowlcdM")\
[Korean pop]("https://open.spotify.com/playlist/30EtqO7XgA36lwcdj1Uuex")

### Energy level comparison

```{r, echo=FALSE}
energy <- ggplot(allPop, aes(x=energy)) +
  geom_histogram(bins=10) +
  theme_minimal() +
  labs(
    x = "Energy Level",
    y = "Amount of songs",
    title = "Korean songs seem to have higher energy songs",
    subtitle = "Comparison of the energy in songs between the two playlists"
  ) +
  facet_wrap(~ playlist_name)

ggplotly(energy)

```

***

When looking at the differences between the energy levels of western pop songs and Korean pop songs you can certainly see a difference.

As is visible in the histogram the mean of the energy of western pop songs is around 0.7, while most of the Korean pop songs have an energy level higher than that. The K-pop songs have a mean energy around 0.85. This shows that K-pop songs have higher energy levels than most of the western songs.

### Chromatic Features of outlier

```{r, echo=FALSE}
more <-
  get_tidy_audio_analysis("6juLaduD4STCUDWT0AYun4") %>%
  select(segments) %>%
  unnest(segments) %>%
  select(start, duration, pitches)

more %>%
  mutate(pitches = map(pitches, compmus_normalise, "chebyshev")) %>%
  compmus_gather_chroma() %>% 
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = pitch_class,
      fill = value
    )
  ) +
  geom_tile() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude", title="Chroma features MORE K/DA") +
  theme_minimal() +
  scale_fill_viridis_c()

```

***

MORE from K/DA is an interesting song as the group K/DA is a virtual group with their real life counterparts being Korean and Western artists. So the songs is made as a collaboration of western and Korean artist and therefore it would be interesting if its possible to see how their styles combine in the music. As is visible in the charts the played notes are definitely pretty consistent. This seems to be more of a western style as it is more common in Korean music to have a lot of switches in the notes. Therefore while it is categorized as K-pop and it is sung by Korean artist the notes and cords still have a Western feel.

